Wiggling the bandwidth

### 2023-01-28 paper.tex
update abstract

\title{Wiggling the bandwidth}
\author{Luca Wellmeier}
\begin{document}
\begin{abstract}
    We explore the possibility of using two different bandwidths in the 
    fitting and evaluation part in kernel ridgeless regression.
    The provided experimental results indicate that \textit{wiggling}
    the bandwidth in this way can provide generalization and potentially 
    be a cheap alternative to the classical Tikhonov square-norm penality.
    Finally, we propose and test a new iterative method for optimizing the 
    bandwidth parameter by employing wiggling in a cheap local parameter 
    search.
\end{abstract}
\maketitle
\tableofcontents

>>>>

\title{Wiggling the bandwidth}
\author{Luca Wellmeier}
\begin{document}
\begin{abstract}
    We explore the possibility of using two different bandwidths in the 
    fitting and evaluation part in kernel ridgeless regression.
    The provided experimental results indicate that \textit{wiggling}
    the bandwidth can provide generalization and improve over standard
    estimators.
    Finally, we propose and test a new iterative method for optimizing the 
    bandwidth parameter by employing wiggling in a cheap local parameter 
    search.
\end{abstract}
\maketitle
\tableofcontents
